---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# ```rrcovHD```: Robust Multivariate Methods for High Dimensional Data

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/rrcovHD)](https://cran.r-project.org/package=rrcovHD)
[![R-CMD-check](https://github.com/valentint/rrcovHD/workflows/R-CMD-check/badge.svg)](https://github.com/valentint/rrcovHD/actions)
[![downloads](https://cranlogs.r-pkg.org/badges/rrcovHD)](https://cran.r-project.org/package=rrcovHD)
[![downloads](https://cranlogs.r-pkg.org/badges/grand-total/rrcovHD)](https://cran.r-project.org/package=rrcovHD)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- badges: end -->

The package ```rrcovHD``` provides robust multivariate methods for high dimensional data including outlier detection (Filzmoser and Todorov (2013) <doi:10.1016/j.ins.2012.10.017>), robust sparse PCA (Croux et al. (2013) <doi:10.1080/00401706.2012.727746>, Todorov and Filzmoser (2013) <doi:10.1007/978-3-642-33042-1_31>), robust PLS (Todorov and Filzmoser (2014) <doi:10.17713/ajs.v43i4.44>), and robust sparse classification (Ortner et al. (2020) <doi:10.1007/s10618-019-00666-8>).
        
## Installation

The `rrcovHD` package is on CRAN (The Comprehensive R Archive Network) and
the latest release can be easily installed using the command

    install.packages("rrcovHD")
    library(rrcovNA)

## Building from source

To install the latest stable development version from GitHub, you can
pull this repository and install it using

    ## install.packages("remotes")
    remotes::install_github("valentint/rrcovHD")

Of course, if you have already installed `remotes`, you can skip the
first line (I have commented it out).

## Example

This is a basic example which shows you if the package is properly installed:

```{r example}

library(rrcovHD)

data(pottery)
dim(pottery)        # 27 observations in 2 classes, 6 variables
head(pottery)

## Build the SIMCA model. Use RSimca for a robust version
rs <- RSimca(origin~., data=pottery)
rs
summary(rs)

```
## Community guidelines

### Report issues and request features

If you experience any bugs or issues or if you have any suggestions for additional features, please submit an issue via the [*Issues*](https://github.com/valentint/rrcovHD/issues) tab of this repository.  Please have a look at existing issues first to see if your problem or feature request has already been discussed.

### Contribute to the package

If you want to contribute to the package, you can fork this repository and create a pull request after implementing the desired functionality.

### Ask for help

If you need help using the package, or if you are interested in collaborations related to this project, please get in touch with the package maintainer.
